\documentclass{article}
\begin{document}
\section{Fall term, Kenneth Thompson:}
\subsection{Week 1} 
This was the first week, we started the new class, had several tasks assigned by our professor, and finished them all in time. It was also a bit of a meet n greet with all our new colleagues to discuss the future of this capstone assignment.
\subsection{Week 2} 
This was the week we received our project, and started contacting the client. We had a few initial hiccups because our client wasn’t answering our emails, but we talked to the professor and coordinated on potential ways to address this.
\subsection{Week 3} 
This week, we finally got our new client and we resolved the issues we’d been having with our old one. As we had become aware, the old client was backing out of the project, leaving us high and dry. We managed to secure a new client and had our first meeting.
\subsection{Week 4} 
This week we began working on our problem statement, and updating it to fit the new requirements that our client wanted. We exchanged a few emails back and forth with the client and we sent them our rough draft and updated drafts to read over and tell us what they thought. He had several notes that we quickly incorporated into our assignment.
\subsection{Week 5} 
Work on documentation that is being required by the client, attend necessary classes, and continue weekly meetings with client to discuss future of project.
\subsection{Week 6} 
Work on documentation that is being required by the client, attend necessary classes, and continue weekly meetings with client to discuss future of project.
\subsection{Week 7} 
Work on documentation that is being required by the client, attend necessary classes, and continue weekly meetings with client to discuss future of project. Deadlines approaching for tech review and design document. 
\subsection{Week 8} 
Worked on our tech review rough draft, talked to client and discussed potential issues, tasked out separate parts of the assignment. We also began testing and debugging some of the code for the project on our own, although we didn’t have any formal deadlines or goals yet.
\subsection{Week 9} 
This was the week that several of our requirements came to a head. We turned in our tech review, turned in our design document, and got final approval on our client to make sure we were submitting something that accurately reflected what he wanted.
\subsection{Week 10} 
Had a quick meeting with our client to discuss plans of action to accomplish over winter break, and then pledged to reconvene in January at the start of winter term. 
\section{Winter term, Kenneth Thompson:}
\subsection{Week 1}
Reconvened for discussions of winter term goals. Reconsolidated the team, got everyone back on the same page, and discussed notes that we accomplished from the winter break. Scheduled more frequent meetings to try and hurry along progress.
\subsection{Week 2}
Worked on our project, confirmed documentation with the client, and assigned out issues on github. Began researching and studying up on proper way to approach those problems. Attended necessary classes. 
\subsection{Week 3}
Began the process of upgrading certain versions of our project and changing out outdated information that was posted during the original project. Testing of new versions being undertaken.
\subsection{Week 4}
Continued the process of upgrading testing and fixing earlier issues. Continued working through outdated documentation and implementing newer more updated documentation. 
\subsection{Week 5}
Continued the process of upgrading testing and fixing earlier issues. Continued working through outdated documentation and implementing newer more updated documentation. Started working on our midterm progress report.
\subsection{Week 6}
Completed the midterm progress report, turned into teacher and client for approval and sign off. Continued working on issues identified earlier. 
\subsection{Week 7}
Client made several request for issues to be addressed, we focused on working our way through those and trying to finish everything up. We began working on data collection improvmenets and increasing the amount of data being fed into the project, we also worked on a blueprint of items to hit in the meeting.
\subsection{Week 8}
We worked on several milestones we wanted to hit before the Beta, and finished up our roadmap to get those done in time. Made a lot of progress, and worked hard to meet our deadlines.
\subsection{Week 9}
Continued working on the items we identified last week, worked hard to accomplish our beta release. 
\subsection{Week 10}
Continued working to finish items assigned by beta release. Finished in time. Broke for spring break with plans to reconvene for spring term and finish out the project.
\section{Spring term, Kenneth Thompson:} 
\subsection{Week 1}
Meeting with professor and client to address issues that had been raised over spring break. Were able to come up with an agreeable roadmap for all parties to be able to complete the project.
\subsection{Week 2}
Stepped up our meeting frequency, worked on new design doc to get approved by client and professor. Have finalized plan for resolving all issues in place so we can finish our project normally.
\subsection{Week 3}
Began working towards new goals, classifier callback, familizarization with the issue, and completing testing. 
\subsection{Week 4}
Begin testing and improving testing functions in code for new sections of code. Committed rough outline of planned functionality.
\subsection{Week 5}
Worked on poster, handed back project to client, stepped away from coding and development. 
\subsection{Week 6}
Worked on pitch then attended and completed expo.
\subsection{Week 7}
Worked on final documentations and closing out project.
\subsection{Week 8}
Worked on final documentations and closing out project.
\subsection{Week 9}
Worked on final documentations and closing out project.
\subsection{Week 10}
Worked on final documentations and closing out project.


\end{document}
